The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2021-09-29 src/paper/data/rapid_test_demand.tex
Polishing.
Add additional references by HiWis to the rapid test demand section.

\begin{enumerate}
    \item someone plans to have work contacts
    \item someone is an employee of an educational facility or a school pupil
    \item a household member has tested positive or developed symptoms
    \item someone has developed symptoms but has not received a PCR test
    \item someone plans to participate in a weekly non-work meeting
\end{enumerate}

@@

In addition, there are some surveys that allow us to trace the expansion of employers who
offer tests to their employees ($\pi_{w,\:s,\:t}$). Mid march, 20\% of employers offered
tests to their employees \citep{DIHK2021}. In the second half of March, 23\% of employees
reported being offered weekly rapid tests by their employer \citep{Ahlers2021}. This
share increased to 61\% until the first days of April \citep{BMWI2021, IZA2021}. Until
mid April 72\% of workers were expected to receive a weekly test offer \citep{BMWI2021,
IZA2021}. However, according to surveys conducted in mid April \citep{Betsch2021}, less
than two thirds of individuals with work contacts receive a test offer. Starting on April
19th employers were required by law to provide two weekly tests to their employees
\citep{Bundesanzeiger2021}. We assume that compliance is incomplete and only 80\% of
employers actually offer tests. We interpolate between these points linearly, arriving at
the blue line in Figure~\ref{fig:rapid_test_demand}. In addition, we increase the
frequency of testing ($\theta_{t,\:work}$) from weekly to twice weekly during April.

>>>>

\begin{enumerate}
    \item someone plans to have work contacts
    \item someone is an employee or student of an educational facility
    \item a household member has tested positive or developed symptoms
    \item someone has developed symptoms but has not received a PCR test
    \item someone plans to participate in a weekly non-work meeting
\end{enumerate}

@@

In addition, there are some surveys that allow us to trace the expansion of employers
who offer tests to their employees ($\pi_{w,\:s,\:t}$). Mid march, 20\% of employers
offered tests to their employees \citep{DIHK2021}. In the second half of March, 23\% of
employees reported being offered weekly rapid tests by their employer
\citep{Ahlers2021}\footnote{\cite{IZA2021b} reports a somewhat higher share of 35\%
around March 20}. This share increased to 61\% until the first days of April
\citep{IZA2021c, IZA2021}. Until mid April 72\% of workers were expected to receive a
weekly test offer \citep{IZA2021c, IZA2021}. However, according to surveys conducted in
mid April \citep{Betsch2021}, less than two thirds of individuals with work contacts
receive a test offer.\footnote{\cite{IZA2021d} report 80\% in mid April which is about
12\% points less than what we arrive at.} Starting on April 19th employers were required
by law to provide two weekly tests to their employees \citep{Bundesanzeiger2021}.
However, compliance was very incomplete and only reached 80\% \citep{IAB2021b,
Ahlers2021b}. We interpolate between these points linearly, arriving at
Figure~\ref{fig:work_rapid_test_offers}. In addition, we increase the frequency of
testing ($\theta_{t,\:work}$) from weekly to twice weekly during April.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/results/figures/data/testing/share_of_workers_with_rapid_test_offer_at_work}
    \caption{Share of Individuals Being Offered a Rapid Test at Work.}
    \floatfoot{\noindent \textit{Note:} Employees were never subject to mandatory tests.
    According to surveys only 60\% of workers regularly used rapid test offers by their
    employers (\cite{Betsch2021}, 20th/21st of April).}
\end{figure}
\FloatBarrier
